### 2018-05-29 Maths Notes/Statistics/S2/Cheat Sheet/S2 Cheat Sheet.tex
S2 Cheat Sheet

@@

@@

@@

>>>>

\subsection{Probability questions involving population parameters}
\textit{Find to 2d.p. the value of k so that $P(\mu-k\sigma<X<\mu+k\sigma)=0.5$}
$$P(-k<Z<k)=0.5$$
$$P(Z=k)=0.75$$

@@

\subsection{Skew}
$$\textrm{Positive skew:} Mean>Median>Mode$$
$$\textrm{Negative skew:} Mean<Median<Mode$$

@@

\setitemize{}

@@

\setitemize{noitemsep,topsep=-5pt,leftmargin=*}
\begin{tabularx}{\textwidth}{|X|X|X|}
&Advantages&Disadvantages\\
Sample survey&
\item If the population is large and well mixed the sample will be representative
\item Cheaper than a census
\item Advantageous when testing results in destruction
\item Data is more readily available
\item Uncertainty as there is variation between samples
\item Could have bias
Census&
\item Every single member of the population is used
\item Unbiased
\item Accurate
\item Time
\item Cost
\item Difficult to ensure the whole population is surveyed
\section{Hypothesis testing}
\setitemize{}
\item \textbf{Critical region} - The range of values such that the null hypothesis is rejected
\item \textbf{Hypothesis test} - A procedure to examine a value of a population parameter proposed by the null hypothesis
\item \textbf{Significance level} - The probability of incorrectly rejecting $H_0$
\subsection{Determining the critical region (from a table)}
Remember to halve the significance level for a two tailed test\\
Small value tail: Find the closest value under the significance level, unless otherwise stated\\
Large value tail: Find the closest value above (1-Sig level), then add one to the value\\
Remember to state the probability in each tail, and the actual critical region using inequalities, not just equations showing the critical values\\
If the distribution has an upper limit, remember to state that too, for example in the binomial distribution, X cannot be greater than n.\\
\textbf{Actual significance} - The sum of the probabilities in the two tails
\subsection{Methods}
\subsubsection{Without normal approximation}
\item Specify $H_0$ and $H_1$
\item Specify the distribution for $X$ under the null hypothesis
\item Determine the probability of the observed value or a more extreme value, or determine the critical region
\item Use the probability to state whether $H_0$ is rejected or not, ensuring you directly compare the probability with the significance level
\item Put the conclusion in context
\subsubsection{With normal approximation}
\item Specify $H_0$ and $H_1$
\item Specify the distribution for $X$ under the null hypothesis
\item Specify the distribution for $Y$ for the normal approximation
\item Do continuity correction
\item Standardise to get a probability in $Z$
\item Compare to the critical values on the data sheet
\item Use the probability to state whether $H_0$ is rejected or not, ensuring you directly compare the probability with the significance level
\item Put the conclusion in context
